Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-14 doc/manuscript/ESSDmanuscript.Rmd
update variables table template
#35

```{r table_variables, eval = TRUE, echo=FALSE, warning=FALSE}
C_variables_table <- read.csv("figures_tables/C_variables.csv")
names(C_variables_table) <- stringr::str_replace_all(names(C_variables_table), "\\.", " ")

library(knitr)
library(kableExtra)
knitr::kable(C_variables_table, format = "latex",
             longtable = FALSE,
             caption = "\\textbf{Numbers of records of ForC variables relevant to, and sent to, EFDB.} Relationships of variables to IPCC-defined forest C pools (Table 1) and to each other are illustrated in Figure 1. ") %>%
  kableExtra::kable_styling(full_width = TRUE) %>%
  row_spec(0, bold = TRUE)
```

>>>>

```{r table_variables, eval = TRUE, echo=FALSE, warning=FALSE}
C_variables_table <- read.csv("figures_tables/C_variables.csv")
names(C_variables_table) <- stringr::str_replace_all(names(C_variables_table), "\\.", " ")
C_variables_table[is.na(C_variables_table)]<- "" #replace NAs with blanks

library(knitr)
library(kableExtra)
knitr::kable(C_variables_table, format = "latex",
             longtable = TRUE,
             caption = "\\textbf{Numbers of records of ForC variables relevant to, and sent to, EFDB.} Relationships of variables to IPCC-defined forest C pools (Table 1) and to each other are illustrated in Figure 1. ") %>%
  kableExtra::kable_styling(full_width = TRUE) %>%
  row_spec(0, bold = TRUE)  %>%
  row_spec(1, bold = TRUE)  %>% #biomass
  row_spec(5, bold = TRUE)  %>% #agb
  row_spec(13, bold = TRUE) %>% #root
  row_spec(21, bold = TRUE)  %>% #dead wood
  row_spec(28, bold = TRUE)  %>% #litter
  row_spec(33, bold = TRUE)  %>% #som
  row_spec(37, bold = TRUE) #total
```

### 2022-04-14 doc/manuscript/ESSDmanuscript.tex
update variables table template
#35

\caption{\label{tab:table_variables}\textbf{Numbers of records of ForC variables relevant to, and sent to, EFDB.} Relationships of variables to IPCC-defined forest C pools (Table 1) and to each other are illustrated in Figure 1. }
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{variable} & \textbf{n in ForC} & \textbf{n independent records in ForC} & \textbf{n reviewed} & \textbf{n sent to EFDB} & \textbf{n posted to EFDB}\\
\hline
STOCKS & NA & NA & NA & NA & NA\\
\hline
biomass & NA & NA & NA & NA & NA\\
\hline
biomass\_ag & NA & NA & NA & NA & NA\\
\hline
biomass\_ag\_foliage & NA & NA & NA & NA & \vphantom{1} NA\\
\hline
biomass\_ag\_woody & NA & NA & NA & NA & NA\\
\hline
biomass\_root & NA & NA & NA & NA & NA\\
\hline
biomass\_root\_fine & NA & NA & NA & NA & NA\\
\hline
biomass\_root\_coarse & NA & NA & NA & NA & NA\\
\hline
deadwood & NA & NA & NA & NA & NA\\
\hline
deadwood\_standing & NA & NA & NA & NA & NA\\
\hline
deadwood\_down & NA & NA & NA & NA & NA\\
\hline
O.horizon & NA & NA & NA & NA & NA\\
\hline
SOM / SOC & NA & NA & NA & NA & NA\\
\hline
INCREMENTS & NA & NA & NA & NA & NA\\
\hline
delta.biomass & NA & NA & NA & NA & NA\\
\hline
delta.agb & NA & NA & NA & NA & NA\\
\hline
biomass\_ag\_foliage & NA & NA & NA & NA & NA\\
\hline
delta.biomass\_root & NA & NA & NA & NA & NA\\
\hline
delta.deadwood & NA & NA & NA & NA & NA\\
\hline
delta.deadwood\_standing & NA & NA & NA & NA & NA\\
\hline
delta.deadwood\_down & NA & NA & NA & NA & NA\\
\hline
delta.O.horizon & NA & NA & NA & NA & NA\\
\hline
delta.SOM / delta.SOC & NA & NA & NA & NA & NA\\
\hline
FLUXES & NA & NA & NA & NA & NA\\
\hline
NPP\_woody & NA & NA & NA & NA & NA\\
\hline
ANPP\_woody\_stem & NA & NA & NA & NA & NA\\
\hline
ANPP\_foliage & NA & NA & NA & NA & NA\\
\hline
BNPP\_root & NA & NA & NA & NA & NA\\
\hline
BNPP\_root\_fine & NA & NA & NA & NA & NA\\
\hline
BNPP\_root\_coarse & NA & NA & NA & NA & NA\\
\hline
woody\_mortality & NA & NA & NA & NA & NA\\
\hline
NPP\_litterfall & NA & NA & NA & NA & NA\\
\hline
R\_het\_litter & NA & NA & NA & NA & NA\\
\hline
R\_het\_soil & NA & NA & NA & NA & NA\\
\hline
TOTAL & NA & NA & NA & NA & NA\\
\hline
\end{tabu}
\end{table}

>>>>

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\caption{\label{tab:table_variables}\textbf{Numbers of records of ForC variables relevant to, and sent to, EFDB.} Relationships of variables to IPCC-defined forest C pools (Table 1) and to each other are illustrated in Figure 1. }\\
\hline
\textbf{variable} & \textbf{n in ForC} & \textbf{n independent records in ForC} & \textbf{n reviewed} & \textbf{n sent to EFDB}\\
\hline
\textbf{Biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass &  &  &  & \\
\hline
delta.biomass &  &  &  & \\
\hline
NPP\_woody &  &  &  & \\
\hline
\textbf{Aboveground biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass\_ag &  &  &  & \\
\hline
biomass\_ag\_woody &  &  &  & \\
\hline
biomass\_ag\_foliage &  &  &  & \\
\hline
delta.agb &  &  &  & \\
\hline
ANPP\_woody\_stem &  &  &  & \\
\hline
ANPP\_foliage &  &  &  & \\
\hline
woody\_mortality &  &  &  & \\
\hline
\textbf{Belowground biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass\_root &  &  &  & \\
\hline
biomass\_root\_fine &  &  &  & \\
\hline
biomass\_root\_coarse &  &  &  & \\
\hline
delta.biomass\_root &  &  &  & \\
\hline
BNPP\_root &  &  &  & \\
\hline
BNPP\_root\_fine &  &  &  & \\
\hline
BNPP\_root\_coarse &  &  &  & \\
\hline
\textbf{Dead wood} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
deadwood &  &  &  & \\
\hline
deadwood\_standing &  &  &  & \\
\hline
deadwood\_down &  &  &  & \\
\hline
delta.deadwood &  &  &  & \\
\hline
delta.deadwood\_standing &  &  &  & \\
\hline
delta.deadwood\_down &  &  &  & \\
\hline
\textbf{Litter} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
O.horizon &  &  &  & \\
\hline
delta.O.horizon &  &  &  & \\
\hline
NPP\_litterfall &  &  &  & \\
\hline
R\_het\_litter &  &  &  & \\
\hline
\textbf{Soil organic matter} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
SOM / SOC &  &  &  & \\
\hline
delta.SOM / delta.SOC &  &  &  & \\
\hline
R\_het\_soil &  &  &  & \\
\hline
\textbf{TOTAL} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
\end{longtabu}
